Verification of concurrent design patterns with data

### 2019-02-13 2018-Arch-pNets/arch-pNets.tex
moved section 4.3

\subsection{SMT encoding of open pNets}
\label{secn:smt}

The encoding into the SMT language involves the definition of the
action and data domains and operators, and the axiomatisation of
domain-dependant properties, to allow the SMT engine to be as precise
as possible (even if it cannot be complete).

The resulting open automaton will later be subject to (symbolic)
model-checking and equivalence checking algorithms, themselves
requiring automatic proof assistance. \todoEM{trop flou pour le
  moment, mais je n'ose pas dire des trucs trop precis... meme si on a
  deja une implem de la FH-bisim, elle n'est pas validee!}

%\noteEMin{Est-ce qu'on a la place de mettre un exemple de script SMT ici ?}

@@

>>>>

% \subsection{SMT encoding of open pNets}
% \label{secn:smt}

@@

%% The encoding into the SMT language involves the definition of the
%% action and data domains and operators, and the axiomatisation of
%% domain-dependant properties, to allow the SMT engine to be as precise
%% as possible (even if it cannot be complete).

%% The resulting open automaton will later be subject to (symbolic)
%% model-checking and equivalence checking algorithms, themselves
%% requiring automatic proof assistance. \todoEM{trop flou pour le
%%   moment, mais je n'ose pas dire des trucs trop precis... meme si on a
%%   deja une implem de la FH-bisim, elle n'est pas validee!}
